|

### 2024-02-27 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
Updating files for IRB

The outcome of interest is a 10-item Likert scale. So the following models will be ordered logistic regressions. Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite vehicle color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information. As the modeling strategy is the same, I include the same confounding variables.

@@

if (params$replicate == TRUE) {
  # Define model arguments
  formula <- brmsformula(
    move ~ RedTreatment + BlueTreatment + PartyID + RedTreatment * PartyID + BlueTreatment * PartyID + age + gender + white + attention
  )
  compiled <- stan_model(
    "./STAN/move_model.stan"
    ,model_name = "moveModel"
  )
  family <- cumulative(link = "logit")
  priors <- prior(
    stats::Normal(0,1)
    ,class = b
  )
    # Run model
  modelDiscrepancies <- sim_all(
    n=c(200, 400, 600, 800)
    , num_samples = 2
    , formula = formula
    , compiled = compiled
    , family = family
    , priors = priors
    , cores = cores
    , model = "moveModel"
  )
    # store model
  save(
      modelDiscrepancies
      , file = "../../data/models/prr/sim/sim.RDS"
  )
} else {
  load(
    file = "../../data/models/prr/sim/sim.RDS"
  )
}
```

>>>>

The outcome of interest is a 10-item Likert scale. So the following models will be ordered logistic regressions. Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite vehicle color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information. Here, I am conducting a triple interaction. As the partisanship of the participants is still not randomized, I include the same confounding variables.

@@

if (params$replicate == TRUE) {
  # Define model arguments
  compiled <- stan_model(
    "./STAN/move_model.stan"
    ,model_name = "moveModel"
  )
    # Run model
  modelDiscrepancies <- sim_all(
    n=c(200, 400, 600, 800)
    , num_samples = 2
    , compiled = compiled
    , cores = cores
    , model = "moveModel"
  )
    # store model
  save(
      modelDiscrepancies
      , file = "../../data/models/prr/sim/sim.RDS"
  )
} else {
  load(
    file = "../../data/models/prr/sim/sim.RDS"
  )
}
```
